Anomalous waves triggered by abrupt depth changes: laboratory experiments and truncated KdV statistical mechanics

### 2020-05-14 paper2_JNLS/Referee Reports/Ref1Response/Ref1.tex
NM

It is conceivable that bound modes could contribute somewhat to the downstream skewness, but we point out that we went to great lengths in the experiments to mitigate the effects of bound modes. In particular, we installed a wave dampener at the far end of the tank, which, after making efforts to optimize our design, we found successful eliminates 90\% of reflections from the far end. See again Bolles et al.~2019 for even more details. It is possible that reflections could be controlled to an even greater degree through electronic feedback systems, such as those present in the Hydrodynamics laboratory facilities at Imperial College of London, but we leave that for future work. It is also conceivable that one could create a data processing method to attempt to filter out the bound modes, but seeing as our theory successful captures the observed skewness transitions, we prefer to avoid the possible ambiguities and uncertainties introduced by an extra layer of data manipulation. 
This is not to say that there is anything wrong with filtering data, it is simply a philosophical position: we aim to develop a parsimonious theory that explains and predicts the experimental data in its raw form, or as close to that as possible.
\end{itemize}

>>>>

It is conceivable that bound modes could contribute somewhat to the downstream skewness, but we point out that we went to great lengths in the experiments to mitigate the effects of bound modes. In particular, we installed a wave dampener at the far end of the tank, which, after making efforts to optimize our design, we found successful eliminates 90\% of reflections from the far end. See again Bolles et al.~2019 for even more details. It is possible that reflections could be controlled to an even greater degree through electronic feedback systems, such as those present in the Hydrodynamics laboratory facilities at Imperial College of London, but we leave that for future work. It is also conceivable that one could create a data processing method to attempt to filter out the bound modes, but seeing as our theory successful captures the observed skewness transitions, we prefer to avoid the possible ambiguities and uncertainties introduced by an extra layer of data manipulation. 
This is not to say that there is anything wrong with filtering data, it is simply a philosophical position: we aim to develop a parsimonious theory that explains and predicts the experimental data in its raw state, or as close to that state as possible.
\end{itemize}
